R Notebook

### 2023-03-02 FEM_R/Loneliness_Social_Isolation/rough_working_script.Rmd
Fixed hotdecking not working properly for lnly, now no more missing values being treated as 0 by the model

```{r}
## Directories
base_output_dir <- "output/COMPLETE/"
input_dir <- "input_data/"
## Inputs
long <- read_dta(paste0(input_dir, 'ELSA_long.dta'))
stock <- read_dta(paste0(input_dir, 'ELSA_stock.dta'))
repl <- read_dta(paste0(input_dir, 'ELSA_repl.dta'))
trans <- read_dta(paste0(input_dir, 'ELSA_transition.dta'))
## Outputs
### Baseline
base <- read_dta(paste0(base_output_dir, 'ELSA_core_base/ELSA_core_base_summary.dta'))
cohort <- read_dta(paste0(base_output_dir, 'ELSA_core_cohort/ELSA_core_cohort_summary.dta'))
### Cross-Validation
cv1 <- read_dta(paste0(base_output_dir, 'ELSA_CV1/ELSA_CV1_summary.dta'))
#cv1.full <- read_dta(paste0(base_output_dir, 'ELSA_CV1/detailed_output/ELSA_CV1_summary.dta'))
cv2 <- read_dta(paste0(base_output_dir, 'ELSA_CV2/ELSA_CV2_summary.dta'))
### Interventions
#no.lonely <- read_dta(paste0(base_output_dir, 'ELSA_nolnly_cohort/ELSA_nolnly_cohort_summary.dta'))
#no.sociso <- read_dta(paste0(base_output_dir, 'ELSA_nosociso_cohort/ELSA_nosociso_cohort_summary.dta'))
#no.lnly.sociso <- read_dta(paste0(base_output_dir, 'ELSA_nolnly_nosociso_cohort/ELSA_nolnly_nosociso_cohort_summary.dta'))
```

>>>>

```{r}
## Directories
base_output_dir <- "output/LNLY_SOCISO_TEST/"
input_dir <- "input_data/"
## Inputs
long <- read_dta(paste0(input_dir, 'ELSA_long.dta'))
stock <- read_dta(paste0(input_dir, 'ELSA_stock.dta'))
repl <- read_dta(paste0(input_dir, 'ELSA_repl.dta'))
trans <- read_dta(paste0(input_dir, 'ELSA_transition.dta'))
## Outputs
### Baseline
base <- read_dta(paste0(base_output_dir, 'ELSA_core_base/ELSA_core_base_summary.dta'))
base.detail <- detailed_output_append(base.out.dir = base_output_dir, scenario = 'ELSA_core_base')
cohort <- read_dta(paste0(base_output_dir, 'ELSA_core_cohort/ELSA_core_cohort_summary.dta'))
### Cross-Validation
#cv1 <- read_dta(paste0(base_output_dir, 'ELSA_CV1/ELSA_CV1_summary.dta'))
#cv1.full <- read_dta(paste0(base_output_dir, 'ELSA_CV1/detailed_output/ELSA_CV1_summary.dta'))
#cv2 <- read_dta(paste0(base_output_dir, 'ELSA_CV2/ELSA_CV2_summary.dta'))
### Interventions
#no.lonely <- read_dta(paste0(base_output_dir, 'ELSA_nolnly_cohort/ELSA_nolnly_cohort_summary.dta'))
#no.sociso <- read_dta(paste0(base_output_dir, 'ELSA_nosociso_cohort/ELSA_nosociso_cohort_summary.dta'))
#no.lnly.sociso <- read_dta(paste0(base_output_dir, 'ELSA_nolnly_nosociso_cohort/ELSA_nolnly_nosociso_cohort_summary.dta'))
```

## LONELINESS

```{r}
lnly.test <- base.detail %>%
  select(hhidpn, year, lnly) %>%
  group_by(year, lnly) %>%
  count()

lnly.test
```

It appears that values of 0 are being assigned to lnly at some point which should not happen! First check the stock dataset and go from there.

```{r}
lnly.stock.test <- stock %>%
  select(idauniq, year, lnly) %>%
  group_by(year, lnly) %>%
  count()

lnly.stock.test

## Try the same in the long files
lnly.long.test <- long %>%
  select(idauniq, year, lnly) %>%
  filter(year == 2012) %>%
  group_by(year, lnly) %>%
  count()

lnly.long.test
```

Appears the lnly values of zero must come from these missing values, first check in stata as R loses the value labels when reading .dta files.

Stata output looking at the long file:

. keep if year == 2012
(88,070 observations deleted)

. tab lnly, m

 Loneliness |
 Score, Low |
to High [1, |
         3] |      Freq.     Percent        Cum.
------------+-----------------------------------
          1 |      5,156       44.96       44.96
          2 |      2,309       20.14       65.10
          3 |        366        3.19       68.29
          . |        866        7.55       75.84
         .c |      2,698       23.53       99.37
         .m |         72        0.63      100.00
------------+-----------------------------------
      Total |     11,467      100.00

Majority of missing cases here are due to not being in the self-completion sample. Makes sense. However what does not make sense is that kludge is not properly imputing the missing values.
